A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-06 tex/sec1-intro.tex
[ tex ] Minor in S1

Type inference is an important mechanism for the transition to well-typed programs from parsed abstract syntax trees, which we call \emph{raw terms}.
Here `type inference' refers specifically to algorithms that ascertain the type of any raw term \emph{without type annotations}.
However, it was later found that full parametric polymorphism leads to undecidability in type inference, as do dependent types~\citep{Wells1999,Dowek1993}.
In light of these limitations, bidirectional type synthesis emerged as a viable alternative, providing algorithms for deciding the types of raw terms that meet some syntactic criteria%
\todo{confirm}
and usually contain some type annotations.
\citet{Dunfield2021} summarised the design principles of bidirectional type synthesis and its wide coverage of languages with simple types, polymorphic types, dependent types, gradual types, among others.

>>>>

Type inference is an important mechanism for the transition to well-typed programs from parsed abstract syntax trees, which we call \emph{raw terms}.
Here `type inference' refers specifically to algorithms that ascertain the type of any raw term \emph{without type annotations}.
However, it was later found that full parametric polymorphism leads to undecidability in type inference, as do dependent types~\citep{Wells1999,Dowek1993}.
In light of these limitations, bidirectional type synthesis emerged as a viable alternative, providing algorithms for deciding the types of raw terms that meet some syntactic criteria and usually contain some type annotations.
\citet{Dunfield2021} summarised the design principles of bidirectional type synthesis and its wide coverage of languages with simple types, polymorphic types, dependent types, gradual types, among others.
